An assessment of the biodiversity - ecosystem function relationship in southern African woodlands

### 2019-11-26 manuscript/chapter_1.tex
Updated models

First, we assessed the interacting factors of structural diversity and species diversity in determining AGB. We constructed a simple mediation model which allowed species diversity to influence AGB both directly and indirectly via structural diversity. To explore variation in the model among woodland vegetation types, we fit the model both at the regional scale and for each vegetation cluster separately. We compared unstandardised path coefficients among these vegetation cluster scale models to understand the effect that vegetation type has on the relationship between tree species diversity, structural diversity, stem density and AGB. Path coefficients show the effect of a path with other paths of inference held constant. Model fit was evaluated using the Comparative Fit Index (CFI), the Tucker Lewis Index (TLI), the Root Mean Squared Error (RMSEA) and the R\textsuperscript{2} coefficient of determination for AGB. We follow t

@@

When the tree species and structural diversity model (\autoref{struc_mod}) was refitted separately using data from each of the 4 vegetation clusters the strengths of unstandardised path coefficients varied but relationships between tree diversity and AGB remained generally similar with the same sign and significant overlap between the 95\% confidence intervals of path coefficients. All models exhibited adequate goodness-of-fit (\autoref{struc_model_fit_clust_stats}), though wide confidence intervals around the unstandardised path coefficients, particularly for Clusters 3 and 4 indicate an issue with model prediction due to low sample size for these clusters.

@@

A model incorporating the latent variables of moisture availability and soil fertility showed that the effect of diversity on biomass was greater than that of both moisture availability and soil fertility (\autoref{full_mod}). Surprisingly, the direct effects of moisture availability and soil fertility on biomass were negligible, with nearly all of their observed effect on AGB coming from the indirect path via species diversity (moisture: \rgmbd{}, soil: \rgsbd{}) (\autoref{full_model_slopes}). MAP and temperature seasonality had the greatest contributions to the latent variable of moisture availability. Model fit was good, CFI = \fmcfi{}, TLI = \fmtli{}, and RMSEA = \fmrmsea{}. The R\textsuperscript{2} coefficient of determination on AGB was \fmrsq{}.

@@

@@

>>>>

First, we assessed the interacting factors of structural diversity and species diversity in determining AGB. We constructed a simple mediation model which allowed species diversity to influence AGB both directly and indirectly via structural diversity. To explore variation in the model among woodland vegetation types, we fit the model both at the regional scale and for each vegetation cluster separately. We compared unstandardised path coefficients among these vegetation cluster scale models to understand the effect that vegetation type has on the relationship between tree species diversity, structural diversity, stem density and AGB. Path coefficients show the effect of a path with other paths of inference held constant. Model fit was evaluated using the Comparative Fit Index (CFI), the Tucker Lewis Index (TLI), the Root Mean Squared Error (RMSEA) and the R\textsuperscript{2} coefficient of determination for AGB.

@@

When the tree species and structural diversity model (\autoref{struc_mod}) was refitted separately using data from each of the 4 vegetation clusters the strengths of unstandardised path coefficients varied but relationships between tree diversity and AGB remained generally similar with the same sign and significant overlap between the 95\% confidence intervals of path coefficients. All models exhibited adequate goodness-of-fit (\autoref{struc_model_fit_clust_stats}), though wide confidence intervals around the unstandardised path coefficients, particularly for Clusters 3 and 4 indicate an issue with model prediction due to low sample size for these clusters. $\chi^{2}$ statistics were high for some vegetation clusters, but this appears to be highly correlated with sample size in our data \citep{}.

@@

A model incorporating the latent variables of moisture availability and soil fertility showed that the effect of diversity on biomass was greater than that of both moisture availability and soil fertility (\autoref{full_mod}). Surprisingly, the direct effects of moisture availability and soil fertility on biomass were negligible, with nearly all of their observed effect on AGB coming from the indirect path via species diversity (moisture: \rgmbd{}, soil: \rgsbd{}) (\autoref{full_model_slopes}). MAP and temperature seasonality had the greatest contributions to the latent variable of moisture availability. Model fit was acceptable: CFI = \fmcfi{}, TLI = \fmtli{}, and RMSEA = \fmrmsea{}. The R\textsuperscript{2} coefficient of determination on AGB was \fmrsq{}.

@@

\todo{C3 had the strongest effect of species div on AGB}

@@

\todo{Maybe at very low stem density, no niche complementarity}

\todo{Decreasing effect of struct. on AGB with stem density}
